Estimating the magnetization distribution within rectangular rock samples

### 2016-06-22 manuscript/manuscript.tex
include tests with data on 1, 2, 3 and 4 planes

Since its beginning in the 1950s, 
palemagnetism has seen at least three generation of rock magnetometers 
(e.g. Turner et al., 2009) FALTA O BIBTEX: astatic systems, 
spinner magnetometers and superconducting magnetometers. 
Astatic system was used during the earliest paleomagnetic studies, 
such as \citet{blackett1952} and Pozzi e Thellier (1960) FALTA O BIBTEX 
and it was quickly replaced by spinner magnetometers (e.g., Nagata, 1961) FALTA O BIBTEX. 
Spinner magnetometers are most used devices in the paleomagnetic 
laboratories but they have been systematically replaced by 
superconducting magnetometers. Superconducting rock magnetometers 
have been developed since 70’s \citep{dodson1974, goree-fuller1976}, 
reaching notable sensitivity and quickness of measurements on the last two decade 
\citep{kirschvink2015}. 
This kind of rock magnetometer can measure both discrete samples 
(single sample mode) and long-core samples (pass-through mode), 
with a good spatial accuracy ($\sim$1 cm).
The long-core samples or u-channel samples are essential to 
investigations of magnetostratigraphy and environmental magnetism, 
such as those ones obtained at IODP (International Ocean Drilling Project).

>>>>

Since its beginning in the 1950s, 
palemagnetism has seen at least three generation of rock magnetometers 
\citep{turner2015}: astatic systems, 
spinner magnetometers and superconducting magnetometers. 
Astatic system was used during the earliest paleomagnetic studies, 
such as \citet{blackett1952} and Pozzi e Thellier (1960) FALTA O BIBTEX 
and it was quickly replaced by spinner magnetometers (e.g., Nagata, 1961) FALTA O BIBTEX. 
Spinner magnetometers are most used devices in the paleomagnetic 
laboratories but they have been systematically replaced by 
superconducting magnetometers. Superconducting rock magnetometers 
have been developed since 70’s \citep{dodson1974, goree-fuller1976}, 
reaching notable sensitivity and quickness of measurements on the last two decade 
\citep{kirschvink2015}. 
This kind of rock magnetometer can measure both discrete samples 
(single sample mode) and long-core samples (pass-through mode), 
with a good spatial accuracy ($\sim$1 cm).
The long-core samples or u-channel samples are essential to 
investigations of magnetostratigraphy and environmental magnetism, 
such as those ones obtained at IODP (International Ocean Drilling Project).
